Energy and the CES production function

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Slight cleanup.

<<CES_sigma_table_data>>=
# This chunk does some preliminary processing
@

@@

<<CES_sigma_nest_aware_inner, results="asis">>=
sigma_inner_data <- filter(table_data, Model=="CES") %>% 
  select(Country, flavor, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
sigma_inner_data <- plyr::rename(sigma_inner_data, c("flavor" = "Factors of prod.",
                                                     "sigma_12" = "$\\sigma_{kl}$",
                                                     "sigma_23" = "$\\sigma_{le}$",
                                                     "sigma_13" = "$\\sigma_{ek}$"))
#
myXTable(sigma_inner_data,
         caption="Factor substitution~($\\sigma$) for inner nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

<<CES_sigma_nest_aware_outer, results="asis">>=
sigma_outer_data <- filter(table_data, Model=="CES") %>% 
  select(Country, flavor, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
sigma_outer_data <- plyr::rename(sigma_outer_data, c("flavor" = "Factors of prod.", 
                                                     "sigma_12_3" = "$\\sigma_{(kl)e}$",
                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
myXTable(sigma_outer_data,
         caption="Factor substitution~($\\sigma$) for outer nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

>>>>

@@

<<CES_sigma_nest_aware_inner, results="asis">>=
sigma_inner_data <- filter(table_data, Model=="CES") %>% 
  select(Country, flavor, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
sigma_inner_data <- plyr::rename(sigma_inner_data, c("flavor" = "Factors of prod.",
                                                     "sigma_12" = "$\\sigma_{kl}$",
                                                     "sigma_23" = "$\\sigma_{le}$",
                                                     "sigma_13" = "$\\sigma_{ek}$"))
#
myXTable(sigma_inner_data,
         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@

@@

<<CES_sigma_nest_aware_outer, results="asis">>=
sigma_outer_data <- filter(table_data, Model=="CES") %>% 
  select(Country, flavor, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
sigma_outer_data <- plyr::rename(sigma_outer_data, c("flavor" = "Factors of prod.", 
                                                     "sigma_12_3" = "$\\sigma_{(kl)e}$",
                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
myXTable(sigma_outer_data,
         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
         label=paste0("tab:", opts_current$get("label")), 
         digits=6)
@
